### 2018-04-24 doc/genesetdp.tex
done?

This enables us to calculate $N$, by nested iterations over $s \in \{ RQ, RQ-1, \ldots 0 \}$ and $c \in \{ Q, Q-1, \ldots 1 \}$ over one single $(RQ+1) \times (Q+1)$ matrix

>>>>

This enables us to calculate $N$, by nested iterations over $s \in \{ RQ, RQ-1, \ldots 0 \}$ and $c \in \{ Q, Q-1, \ldots 1 \}$ over one single $(RQ+1) \times (Q+1)$ matrix.

\subsection*{$p$ value calculation}

Once we have our full score distribution, we can evaluate our score against the null hyptesis, $H_0$ : ``The Q query genes are random''. This can be expressed as an unbiased empirical $p$~value for obtaining a score $s$,

\[
p(s)=\frac{N(s')/2 +\sum_{s'=s+1}^{RQ} N(s')}{\sum_{s'=0}^{RQ} N(s')}
\]
